\section{Per-Job environment files}
\subsection{scheduler.conf} \hfill \\
The file \filename{scheduler.conf} is a  \javaapi{java.util.Properties} file \footnote{See: \javaapi{java.util.Properties} and \wikipedia{.properties} } containing information from the front-end and middle-ware about how a job is to be scheduled. This is the natural home for future information about scheduling, for example if the queue is to be selected explicitly.
This file stores (key, value) pairs of Strings. It is up to the creator and client to enforce any datatypes other than that.

Currently, \filename{scheduler.conf} may contain any of the following entries:

\begin{longtable}{|r||p{.2\textwidth}|p{.15\textwidth}|p{ .3\textwidth} | }
\caption{Allowed values in \filename{scheduler.conf}}\\
\hline
{\bf Name} & {\bf Allowed Values} & {\bf Default if missing} &  {\bf Notes}\\
\hline
jobtype & NIL, ``direct" , ``mpi", ``serial'' & ``serial" & ``serial" is also used for shared-memory parallel jobs. \\
mpi\_processes & NIL, 1, 2, 3, ...& 1 & Shared memory and serial jobs should be considered to have 1 mpi process. \\
threads\_per\_process & NIL, 1, 2, 3, ...  & 1 & Used to control hybrid MPI tasks and shared-memory parallel tasks.\\
runhours & $(0.0 , \inf)$ & No Default, required. & A float, giving the maximum wall-time in hours.\\
node\_exclusive & NIL, 0, 1 & 0 & Binary encoded boolean value. Set to ``1" to force node-exclusive scheduling\\
\hline
\multicolumn{4}{||c||}{The following are reserved for \theprog to set, or future use.}\\
\hline
nodes & NIL, 1, 2, 3 & No default & This is generally calculated by \theprog, and is thus currently ignored from the front-end.\\
ppn & 1, 2, 3, ... & 1 & \\
queue & Any String & No default & It is a primary feature of \theprog to choose this. May be used in the future to force a certain queue.\\
\hline 
\end{longtable}


\pagebreak
\subsection{\_JOBINFO.TXT\label{jobinfo}} \hfill \\
The file \filename{\_JOBINFO.TXT} is a  \javaapi{java.util.Properties} file \footnote{See: \javaapi{java.util.Properties} and \wikipedia{.properties} } containing information from the front-end and middle-ware about what job is to be run, on what resource, with what names, the {\em portal } jobID etc.
This file stores (key, value) pairs of Strings. It is up to the creator and client to enforce any datatypes other than that.

The file is created in {\bf org.ngbw.sdk.tool.BaseProcessWorker}.

Currently, \filename{\_JOBINFO.TXT} may contain any of the following entries: \\
({\bf Warning: } This list may be incomplete!)

\begin{longtable}{|r||p{.2\textwidth}|p{.15\textwidth}|p{ .3\textwidth} | }
\caption{Allowed values in \filename{\_JOBINFO.TXT}}\\
\hline
{\bf Name} & {\bf Datatype} & {\bf Default if missing} &  {\bf Notes}\\
\hline
Task label & String & Required & Note that names with spaces must have those spaces escaped with a ``\textbackslash" character, if a .properties file is written directly.\\
Task ID & int & Required & See above.\\
Tool & String & Required & \theprog reads this.\\
created on & ``YYYY-MM-DD HH:MM:SS.s" & Required & Hours are 24 hour, ``s" denotes the tenth of a second.\\
JobHandle & NGBW Job identifier (String) & Required & \\
resource & String & Required & {\bf Important, used to determine the resource to template for.}\\
User ID & int & Required & NGBW or Portal userid?\\
User Name & String & Required & NGBW or Portal username?\\
email & E-Mail address & Required ? & NGBW or Portal user e-mail address, not used for job notification via ``qsub -M $<$ email $>$"\\
Output & String & ? & Currently Ignored by \theprog\\
JOBID & String & Starts Empty &Set by \theprog \\
\hline 
\end{longtable}
